A Kochen-Specker system has at least 22 vectors

### 2014-12-14 paper/main.tex
paper: move AOW's graph to the right

We have verified the main result of \cite{aow11}:
\begin{comp}
There is a unique non-010-colorable squarefree connected graph on~$17$ or less
vertices:
\begin{center}
    \begin{tikzpicture}[thick,scale=1.4,
        p/.style={circle, draw, fill=white,
                        inner sep=0pt, minimum width=5pt}]
        \draw
            \foreach \x in {0,90,180,270} {
                (\x+45:1) node[p]{} -- (\x+65:1.3) node[p]{}
                (\x+45:1)  -- (\x+25:1.3) node[p]{}
                (\x+65:1.3)  -- (\x+25:1.3)
            }
            \foreach \x in {0,180} {
                (\x:0.8) node[p]{} -- (\x+25:1.3)
                (\x:0.8) -- (\x-25:1.3)
                (\x+25:1.3) -- (\x-25:1.3)
                (\x+65:1.3) -- (\x+115:1.3)
            }
            (0:0.8) -- (180:0.8)
            (90:0.2) node[p]{} -- (0:0.8)
            (90:0.2) -- (180:0.8)

            (90:0.2) -- (90:0.6) node[p]{}
            (90:0.6) -- (270+45:1)
            (90:0.6) -- (270-45:1)
            (90:0.6) -- (90+45:1)
            (90:0.6) -- (90-45:1)

            (90:0.2) -- (270:0.4) node[p]{}
            (270:0.4) -- (270+25:1.3)
            (270:0.4) -- (270-25:1.3)
            (270:0.4) -- (90+25:1.3)
            (270:0.4) -- (90-25:1.3)
        ;
    \end{tikzpicture}
\end{center}
It is not embeddable, as the graph in Figure~\ref{fig:unemb-10-2}
is an unembeddable subgraph.  For our proof,
see Proposition~\ref{prop:unemb-10-2}.
Hence a Kochen-Specker
system has at least 18 points.
\end{comp}

>>>>

We have verified the main result of \cite{aow11}:

\piccaption{AOW's 17-vertex non-010-colorable graph\label{fig:noncol17}}
\parpic[r]{%
    \begin{tikzpicture}[thick,scale=1.4,
        p/.style={circle, draw, fill=white,
                        inner sep=0pt, minimum width=5pt}]
        \draw
            \foreach \x in {0,90,180,270} {
                (\x+45:1) node[p]{} -- (\x+65:1.3) node[p]{}
                (\x+45:1)  -- (\x+25:1.3) node[p]{}
                (\x+65:1.3)  -- (\x+25:1.3)
            }
            \foreach \x in {0,180} {
                (\x:0.8) node[p]{} -- (\x+25:1.3)
                (\x:0.8) -- (\x-25:1.3)
                (\x+25:1.3) -- (\x-25:1.3)
                (\x+65:1.3) -- (\x+115:1.3)
            }
            (0:0.8) -- (180:0.8)
            (90:0.2) node[p]{} -- (0:0.8)
            (90:0.2) -- (180:0.8)
            (90:0.2) -- (90:0.6) node[p]{}
            (90:0.6) -- (270+45:1)
            (90:0.6) -- (270-45:1)
            (90:0.6) -- (90+45:1)
            (90:0.6) -- (90-45:1)
            (90:0.2) -- (270:0.4) node[p]{}
            (270:0.4) -- (270+25:1.3)
            (270:0.4) -- (270-25:1.3)
            (270:0.4) -- (90+25:1.3)
            (270:0.4) -- (90-25:1.3)
        ;
    \end{tikzpicture}}

\begin{comp}
There is only one non-010-colorable squarefree connected graph
on less than~$18$ vertices.  See Figure~\ref{fig:noncol17}.
It is not embeddable, as the graph in Figure~\ref{fig:unemb-10-2}
is an unembeddable subgraph.  For our proof,
see Proposition~\ref{prop:unemb-10-2}.
Hence a Kochen-Specker
system has at least 18 points.
\end{comp}
